Lifting CDCL to Numerical Domains

### 2016-10-05 deductions.tex
git update

A {\em worklist} is initialized following a heuristics choice for iteration 
strategies. A {\em forward} iteration strategy initializes the worklist with 
transformers that has constants in the right-hand side. Whereas, a {\em backward} 
iteration strategy starts with a set of assertions. On the other hand, a 
{\em chaotic} iteration strategy initializes the worklist with set of all 
transformers.  For every meet irreducible deduction transformer $s \in S$ 
passed to the abstract domain, if the domain infers a new meet irreducible 
$\mathit{meet\_irrd}$, it is added to $\mathcal{T}$.  Additionally, the reason 
trail $\mathcal{R}$ is updated with the transformer $s$ as the reason for inferring
$\mathit{meet\_irrd}$. If a conflict is deduced, that is, $\mathit{meet\_irrd} = \bot$ 
is inferred by the domain, the algorithm terminates with UNSAT.  However,
when a fixed-point is reached, the abstract value $v$ is checked for set of
models.  This is done by checking whether the set of assignments in $v$ is 
$\gamma$-complete~\cite{gamma}.  If $v$ is $\gamma$-complete, the abstract model 
search terminates with SAT.  Otherwise, a decision is made by calling a 
procedure $decide(v)$ which returns a meet irreducible $d$.  If $d$ refines the 
current abstract value $v$, then the corresponding propagation and reason trail,
$\mathcal{T}$ and $\mathcal{R}$, are updated. Else, the algorithm terminates
with UNKNOWN.      
%    
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{deduce}{deduce}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwData{sat}{SAT}
\SetKwData{unsat}{UNSAT}
\SetKwData{unknown}{UNKNOWN}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKwFor{Loop}{Loop}{}{}
\SetKw{KwNot}{not}
\begin{small}
\Input{Set $S$ of $\widehat{ded_{\varphi}}$ for $\varphi$ over Abstract domain $A$,
abstract value $v$, propagation trail $\mathcal{T}$, reason trail $\mathcal{R}$}
\Output{The status (\sat or \unsat or \unknown)}
worklist $\leftarrow$ initialize\_worklist($S$) \;
\Loop{}
{
// Greatest fixed point \;
\While{$!worklist.empty()$} 
{
  $\langle live\_vars, s \rangle \leftarrow$ worklist.pop() \;
  $\mathit{meet\_irrd} \leftarrow$ domain(s, live\_vars, $v$)\;
  // check if the domain deduce BOTTOM \;
  \uIf{$meet\_irrd == \bot$} {
    $\mathcal{R}[\bot] \leftarrow s$ \;
    // empty the worklist \;
    worklist.delete() \;
    \return \sat \;
  }
  \uElse
  {
    // add deduction to trail \;
    $\mathcal{T} \leftarrow \mathcal{T} . \mathit{meet\_irrd}$ \; 
    $v \leftarrow v \meet \mathit{meet\_irrd}$ \; 
    $\mathcal{R}[|\mathcal{T}|] \leftarrow s$ \;
    // update the worklist \;
    worklist.update(v, s) \; 
  }
}
// check for counterexample\;
\uIf{$v$ is $\gamma$-complete} {
  \return \unsat;
}
$d \leftarrow decide(v)$ \;
\uIf{$v \sqsubseteq d$} {
\return \unknown \;
}
// add decision to trail\;
$\mathcal{T} \leftarrow \mathcal{T} . d$ \; 
$v \leftarrow v \meet d$ \; 
$\mathcal{R}[|\mathcal{T}|] \leftarrow nil$ \;
}
\end{small}
\caption{Abstract Model Search Procedure\label{Alg:ms}}
\end{algorithm2e}
%
\subsection{Forward Iteration Strategy}
For forward iteration on Figure~\ref{swssa}, we need atleast 
one decision to deduce BOTTOM and prove safety. The deduction 
happens from right to left in forward iteration strategy.

The initialization of live variable and subsequent update depends on the iteration strategy.

\subsection{Backward Iteration Strategy}

\subsection{Chaotic Iteration Strategy}  
The set of octagonal equilities corresponding to Figurei~\ref{sw-ssa}
is shown below. For chaotic, no decision is required to deduce BOTTOM.

\Omit {
Let us consider an example. 
\begin{figure}[t]
\scriptsize
\begin{tabular}{l|l|l}
\hline
C program & SSA & Octagons \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
int id(int a) {
  return a;
}
int main() {
 int x,y,z;
 _Bool c;
 if (c)
   x = -1;
 else
   x = 2;
 int k = id(x);
 z = x * k;
 assert((z!=-2));
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
cond == (x == y)
guard1 == (cond19 && guard0)
x' == 1u + x
x' == 1u + y || !guard1
guard0 == TRUE
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]

\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program, corresponding SSA and Octagonal inequalities}
\label{swssa}
\end{figure}
}

With forward iteration strategy using octagon domian, the program 
is proved without any decision. However, with the forward strategy
using interval domain, we just required one decision to prove the program.

>>>>

A {\em worklist} is initialized following a heuristics choice for iteration 
strategies. A {\em forward} iteration strategy initializes the worklist with 
transformers that has constants in the right-hand side. Whereas, a {\em backward} 
iteration strategy starts with a set of assertions. On the other hand, a 
{\em chaotic} iteration strategy initializes the worklist with set of all 
transformers.  For every meet irreducible deduction transformer $s \in S$ 
passed to the abstract domain, if the domain infers a new meet irreducible 
$\mathit{meet\_irrd}$, it is added to $\mathcal{T}$.  Additionally, the reason 
trail $\mathcal{R}$ is updated with the transformer $s$ as the reason for inferring
$\mathit{meet\_irrd}$. If a conflict is deduced, that is, $\mathit{meet\_irrd} = \bot$ 
is inferred by the domain, the algorithm terminates with UNSAT.  However,
when a fixed-point is reached, the abstract value $v$ is checked for set of
models.  This is done by checking whether the set of assignments in $v$ is 
$\gamma$-complete~\cite{gamma}.  If $v$ is $\gamma$-complete, the abstract model 
search terminates with SAT.  Otherwise, a decision is made by calling a 
procedure $decide(v)$ which returns a meet irreducible $d$.  If $d$ refines the 
current abstract value $v$, then the corresponding propagation and reason trail,
$\mathcal{T}$ and $\mathcal{R}$, are updated. Else, the model search procedure terminates with UNKNOWN.      
%    
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{deduce}{deduce}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwData{sat}{SAT}
\SetKwData{unsat}{UNSAT}
\SetKwData{unknown}{UNKNOWN}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKwFor{Loop}{Loop}{}{}
\SetKw{KwNot}{not}
\begin{small}
\Input{Set $S$ of $\widehat{ded_{\varphi}}$ for $\varphi$ over Abstract domain $A$,
abstract value $v$, propagation trail $\mathcal{T}$, reason trail $\mathcal{R}$}
\Output{The status (\sat or \unsat or \unknown)}
worklist $\leftarrow$ initialize\_worklist($S$) \;
\Loop{}
{
// Greatest fixed point \;
\While{$!worklist.empty()$} 
{
  $\langle live\_vars, s \rangle \leftarrow$ worklist.pop() \;
  $\mathit{meet\_irrd} \leftarrow$ domain(s, live\_vars, $v$)\;
  // check if the domain deduce BOTTOM \;
  \uIf{$meet\_irrd == \bot$} {
    $\mathcal{R}[\bot] \leftarrow s$ \;
    // empty the worklist \;
    worklist.delete() \;
    \return \sat \;
  }
  \uElse
  {
    // add deduction to trail \;
    $\mathcal{T} \leftarrow \mathcal{T} . \mathit{meet\_irrd}$ \; 
    $v \leftarrow v \meet \mathit{meet\_irrd}$ \; 
    $\mathcal{R}[|\mathcal{T}|] \leftarrow s$ \;
    // update the worklist \;
    worklist.update(v, s) \; 
  }
}
// check for counterexample\;
\uIf{$v$ is $\gamma$-complete} {
  \return \unsat;
}
$d \leftarrow decide(v)$ \;
\uIf{$v \sqsubseteq d$} {
\return \unknown \;
}
// add decision to trail\;
$\mathcal{T} \leftarrow \mathcal{T} . d$ \; 
$v \leftarrow v \meet d$ \; 
$\mathcal{R}[|\mathcal{T}|] \leftarrow nil$ \;
}
\end{small}
\caption{Abstract Model Search Procedure\label{Alg:ms}}
\end{algorithm2e}
%
